\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-23 journalWallFriction/theory2robAlgs.tex
This draft contains all the required results.

Workspaces are 2D convex polygons with no internal obstacles. 
 Assume two particles are initialized at $s_1$ and $s_2$ with corresponding goal destinations $g_1$ and $g_2$. 
Denote the current positions of the particles  $p_1$ and $p_2$

@@

 Given an $n$-sided convex polygon $P$, the $\Delta$ configuration space is an $2n$-sided convex polygon.
 A special case is for even-sided regular polygons, in which half the sides align and the $\Delta$ configuration space  is $n$-sided.

 \textcolor{red}{[INSERT PROCEDURE]}\\

 \textcolor{red}{    Describe how to generate a $\Delta$ Configuration Space for polygon $P$.}

% \textcolor{red}{[INSERT ONE IMAGE OF A 4-sided irregular convex polygon]}\\
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{irregular.pdf}\end{overpic}
\caption{\label{fig:irregular}
Workspace and $\Delta$ configuration space is shown for an arbitrary convex polygon with $n=4$ sides. The 2-side reachable sets are drawn in transparent blue.
}
\end{figure}

>>>>

Workspaces are 2D convex polygons with no internal obstacles. 
 Assume two particles are initialized at $s_1$ and $s_2$ with corresponding goal destinations $g_1$ and $g_2$. 
Denote the current positions of the particles  $p_1$ and $p_2$.

@@

 $\Delta$ configuration space is a space containing all the possible relative distances for $p_1$ and $p_2$. Given an $n$-sided convex polygon $P$, the $\Delta$ configuration space is a $2n$-sided convex polygon.
 A special case is for even-sided regular polygons, in which half the sides align and the $\Delta$ configuration space  is $n$-sided. 
 To give an intuition what $\Delta$ configuration space is, consider the first particle on a vertex of the workspace. Now if the other particle moves on the boundary of the workspace, the relative distance between the two particles is maximized. Consider the first particle is fixed at (0,0). To generate the $\Delta$ configuration space we iterate through all the vertices, $i$ and consider that first particle is positioned at $i^{\textrm{th}}$ vertex. To find all possible $\Delta p$ values, compute $v_i - v_j$ where $j$ goes from 1 to $n$. For each vertex, $i$, we have made one $n$-sided polygon defined by its vertices. The outer boundary of all these polygons shows the boundary of the $\Delta$ configuration space. Fig.~\ref{fig:irregular} shows an arbitrary 4-sided workspace on the left. All the polygons made by $p_1$ and $p_2$ are shown in the middle. $\Delta$ configuration space is shown on the right with 2-move reachable sets drawn in transparent blue. We discuss how to generate 2-step reachable sets in the following subsection.

 %\textcolor{red}{[INSERT PROCEDURE]}\\

 %\textcolor{red}{    Describe how to generate a $\Delta$ Configuration Space for polygon $P$.}

% \textcolor{red}{[INSERT ONE IMAGE OF A 4-sided irregular convex polygon]}\\
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{irregular.pdf}\end{overpic}
\caption{\label{fig:irregular}
Workspace and $\Delta$ configuration space is shown for an arbitrary convex polygon with $n=4$ sides. The 2-move reachable sets are drawn in transparent blue.
}
\end{figure}
